---
title: "ML03_glmnet_abstract"
author: "Jilung Hsieh"
date: "11/17/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# loading library
```{r}
set.seed(1)
# install.packages("glmnet")
library(glmnet)
?glmnet
```


## ?glmnet
- `alpha=1` is the lasso penalty, and `alpha=0` the ridge penalty.

```
glmnet(x, y, 
    family=c("gaussian","binomial","poisson","multinomial","cox","mgaussian"),
    weights, offset=NULL, alpha = 1, nlambda = 100,
    lambda.min.ratio = ifelse(nobs<nvars,0.01,0.0001), lambda=NULL,
    standardize = TRUE, intercept=TRUE, thresh = 1e-07,  dfmax = nvars + 1,
    pmax = min(dfmax * 2+20, nvars), exclude, penalty.factor = rep(1, nvars),
    lower.limits=-Inf, upper.limits=Inf, maxit=100000,
    type.gaussian=ifelse(nvars<500,"covariance","naive"),
    type.logistic=c("Newton","modified.Newton"),
    standardize.response=FALSE, type.multinomial=c("ungrouped","grouped"))

```


# One pass test
- Pre-defining lambda to 0.001

```{r}
stime <- Sys.time()
glm.fit <- glmnet(train.df %>% select(-sentence_type, -sentence_id) %>% as.matrix(), 
                  as.factor(train.df$sentence_type), 
                  family = 'multinomial')
Sys.time() - stime

predicted.df <- predict(glm.fit, 
                       test.df %>% select(-sentence_id, -sentence_type) %>% as.matrix(), 
                       s = 0.0025) %>%  
    as.data.frame() %>% View
    bind_cols(test.df %>% select(sentence_id)) %>%
    select(sentence_id,
           BACKGROUND=BACKGROUND.1, 
           CONCLUSIONS=CONCLUSIONS.1, 
           METHODS=METHODS.1, 
           OBJECTIVES=OBJECTIVES.1, 
           RESULTS=RESULTS.1) %>%
    gather(predicted_type, value, -sentence_id) %>%
    group_by(sentence_id) %>%
    arrange(-value) %>%
    slice(1:1) %>%
    ungroup() %>%
    left_join(test.df %>% select(sentence_id, sentence_type), by = "sentence_id")

conf.mat <- table(Prediction = predicted.df$predicted_type, Actual = predicted.df$sentence_type)
conf.mat %>% as_tibble %>% spread(Actual, n)
(accuracy <- sum(diag(conf.mat))/sum(conf.mat) * 100)
```


# Regularization

> [1] "[Iteration 1 with lambda 1e-04] Accuracy:  50.1750547045952"
> [1] "[Iteration 1 with lambda 0.001] Accuracy:  51.2691466083151"
> [1] "[Iteration 1 with lambda 0.0025] Accuracy:  52.1006564551422"
> [1] "[Iteration 1 with lambda 0.005] Accuracy:  51.925601750547"
> [1] "[Iteration 1 with lambda 0.01] Accuracy:  50.8752735229759"
> [1] "[Iteration 1 with lambda 0.025] Accuracy:  29.1028446389497"
> [1] "[Iteration 1 with lambda 0.5] Accuracy:  27.1115973741794"
> [1] "[Iteration 1 with lambda 0.1] Accuracy:  28.5120350109409"

```{r}
performance <- tibble()

for (i in 1:10){
    
    index <- sample(1:nrow(mat.df), ceiling(nrow(mat.df) * .70))
    train.df <- mat.df[index, ]
    test.df <- mat.df[-index, ]

    
    for (lambda in c(0.0001, 0.001, 0.0025, 0.005, 0.01, 0.025, 0.5, 0.1)){
        glm.fit <- glmnet(train.df %>% select(-sentence_type, -sentence_id) %>% as.matrix(), 
                          as.factor(train.df$sentence_type), 
                          family = 'multinomial')
        
        predicted.df <- predict(glm.fit, 
                                test.df %>% select(-sentence_id, -sentence_type) %>% as.matrix(), 
                                s = lambda) %>%  
            as.data.frame() %>%
            bind_cols(test.df %>% select(sentence_id)) %>%
            select(sentence_id,
                   BACKGROUND=BACKGROUND.1, 
                   CONCLUSIONS=CONCLUSIONS.1, 
                   METHODS=METHODS.1, 
                   OBJECTIVES=OBJECTIVES.1, 
                   RESULTS=RESULTS.1) %>%
            gather(predicted_type, value, -sentence_id) %>%
            group_by(sentence_id) %>%
            arrange(-value) %>%
            slice(1:1) %>%
            ungroup() %>%
            left_join(test.df %>% select(sentence_id, sentence_type), by = "sentence_id")
        
        conf.mat <- table(Prediction = predicted.df$predicted_type, Actual = predicted.df$sentence_type)
        conf.mat %>% as_tibble %>% spread(Actual, n)
        accuracy <- sum(diag(conf.mat))/sum(conf.mat) * 100
        print(str_interp("[Iteration ${i} with lambda ${lambda}] Accuracy:  ${accuracy}"))
        
        performance <- bind_rows(performance,
                             data.frame(Lambda = lambda,
                                        Iteration = i,
                                        Accuracy = accuracy))
    }
    print(i)
}
??glmnet
```


```{r}
glm.fit
```
```{r}

?stat_summary
# install.packages("Hmisc")
library(Hmisc)
ggplot(performance, aes(x = Lambda, y = Accuracy)) + stat_summary(fun.data = 'mean_cl_boot', geom = 'errorbar') + stat_summary(fun.data = 'mean_cl_boot', geom = 'point') + scale_x_log10()

```

