1--- title: "R03_1\_base_to_dplyr_maternal_leave" author: "Jilung Hsieh" date: "3/4/2022" output: html_document ---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading library

當第一次載入`tidyverse`時所印出的資訊即為載入`tidyverse`所會自動載入的套件，所以不用再額外載入這些套件。例如：`ggplot`、`readr`、`stringr`、`lubridate`等。

```{r}
library(tidyverse)
# ── Attaching core tidyverse packages ────────────── tidyverse 2.0.0 ──
# ✔ dplyr     1.1.0     ✔ readr     2.1.4
# ✔ forcats   1.0.0     ✔ stringr   1.5.0
# ✔ ggplot2   3.4.1     ✔ tibble    3.1.8
# ✔ lubridate 1.9.2     ✔ tidyr     1.3.0
# ✔ purrr     1.0.1     ── Conflicts ────────── tidyverse_conflicts() ──
# ✖ dplyr::filter() masks stats::filter()
# ✖ dplyr::lag()    masks stats::lag()
# ℹ Use the conflicted package to force all conflicts to become errors
```

過去的R會預設將字串（string）轉為factor，但現在的R 4.0版本已經預設保留字串格式。如果使用比較低的R版本，通常會為了避免預設轉為factor，會加上`options(stringsAsFactors = F)`，這是一個全域（global）的預設設定，凡是任何函式有`stringsAsFactors`的都會預設為`F`。

```{r}
library(readxl)
# options(stringsAsFactors = F)
```

# Original Version

```{r}
# readxl::read_excel() to import the xls file
df <- read_excel("data/WORLD-MACHE_Gender_6.8.15.xls", "Sheet1", col_names=T)

# select iso3, and matleave columns by index
matleave <- df[ , c(3, 6:24)]

# select all NA cells and assign 0 to them
matleave[is.na(matleave)] <- 0

# filter rows by condition
m5 <- matleave[matleave$'matleave_13' == 5, ]

# filter rows by condition
m55<- m5[m5$'matleave_95' == 5,]

# plot
par(mfrow=c(4,6), mai= c(0.2, 0.2, 0.2, 0.2))
for (i in c(1:nrow(m55))){
    barplot(unlist(m55[i,-1]),
            border=NA, space=0,xaxt="n", yaxt="n", ylim = c(0,5))
    title(m55[i,1], line = -4, cex.main=3)
}
```

# Tidyverse version

## Loading data

```{r}
raw <- read_excel("data/WORLD-MACHE_Gender_6.8.15.xls", "Sheet1", col_names=T)
```

## Select and filter data

```{r}

# Select the iso3 variable and 6th to 24th variables
matleave <- 
    
# filter matleave_13==5
m5 <- 

# filter matleave_95==5
m55 <- 
    
```

## Using pipeline

```{r}
# Rewrite by pipeline and assign to m55
read_excel("data/WORLD-MACHE_Gender_6.8.15.xls", "Sheet1", col_names=T)
```


## Now ask chatgpt
Q: "I have a data frame with iso3 codes in the first column and year values ranging from 1995 to 2013 in the second to twentieth columns. I would like to convert this wide-format table to a long-format table with three columns: iso3, year, and corresponding value from the original wide-format table. How can I accomplish this?"

ChatGPT "You can use the pivot_longer() function from the tidyr package to convert a wide table to a long table in R. Here's an example code that shows how to do this with your data:"

```{r}
library(tidyr)

# Create a sample data frame
df <- data.frame(
  iso3 = c("USA", "CAN", "MEX"),
  `1995` = c(10, 20, 30),
  `1996` = c(15, 25, 35),
  `1997` = c(20, 30, 40)
)

# Convert the data frame from wide to long format
df_long <- pivot_longer(
  data = df, 
  cols = starts_with("19"), 
  names_to = "year", 
  values_to = "value"
)

# View the converted data frame
df_long
```

```{r}
read_excel("data/WORLD-MACHE_Gender_6.8.15.xls", "Sheet1", col_names=T) %>%
	select(iso3, contains("matleave"), -contains("wrr")) %>%
	filter(matleave_13==5, matleave_95!=5) %>%
	pivot_longer(names_to = "year", cols = 2:20, values_to = "degree")
```

# ChatGPT practice

The following is your ChatGPT task. Here is the complete working code. After understanding the code, how would you ask ChatGPT to explain the following three lines of code? Please try to write your questions to ChatGPT in this RMD document. Perhaps you can start by asking what the meaning of these three lines of code is.

## Question1
Q: 
ChatGPT: 
Q: 
ChatGPT: 

## Question2
Q: 
ChatGPT: 

## Question3
Q: 
ChatGPT: 


# Working tidyverse version

```{r}
library(readxl)

read_excel("data/WORLD-MACHE_Gender_6.8.15.xls", "Sheet1", col_names=T) %>%
	select(iso3, contains("matleave"), -contains("wrr")) %>%
	filter(matleave_13==5, matleave_95!=5) %>%
	pivot_longer(names_to = "year", cols = 2:20, values_to = "degree") %>%
	replace_na(list(degree=0)) %>%
	mutate(year2=as.POSIXct(strptime(year, "matleave_%y"))) %>%
	mutate(year3 = strftime(year2, "%Y")) %>%
	ggplot() +
	aes(year3, degree) +
    geom_col(color="royalblue", fill="royalblue") + 
	facet_wrap(~ iso3) + 
    theme_void()
```

# Run following code chunks to see what you get

## 1. Read EXCEL

```{r}
read_excel("data/WORLD-MACHE_Gender_6.8.15.xls", "Sheet1", col_names=T) %>%
    View
```

## 2. Select data

### Select one column

```{r}
read_excel("data/WORLD-MACHE_Gender_6.8.15.xls", "Sheet1", col_names=T) %>%
	select(iso3)
```

### Select by index

```{r}
read_excel("data/WORLD-MACHE_Gender_6.8.15.xls", "Sheet1", col_names=T) %>% 
	select(3, 6:24)
```

### Select by `contains()`

```{r}
read_excel("data/WORLD-MACHE_Gender_6.8.15.xls", "Sheet1", col_names=T) %>%
	select(iso3, contains("matleave"), -contains("wrr")) %>% View
```

## 3. Filter data

```{r}
read_excel("data/WORLD-MACHE_Gender_6.8.15.xls", "Sheet1", col_names=T) %>%
	select(iso3, contains("matleave"), -contains("wrr")) %>%
	filter(matleave_13==5, matleave_95!=5)
```

## 4. Convert wide- to long-table

```{r}
read_excel("data/WORLD-MACHE_Gender_6.8.15.xls", "Sheet1", col_names=T) %>%
	select(iso3, contains("matleave"), -contains("wrr")) %>%
	filter(matleave_13==5, matleave_95!=5) %>%
	gather("year", "degree", 2:20)

```

## 5. Cleaning: replace `NA`

```{r}
read_excel("data/WORLD-MACHE_Gender_6.8.15.xls", "Sheet1", col_names=T) %>%
	select(iso3, contains("matleave"), -contains("wrr")) %>%
	filter(matleave_13==5, matleave_95!=5) %>%
	pivot_longer(names_to = "year", cols = 2:20, values_to = "degree") %>%
	replace_na(list(degree=0))
```

## 6. Mutate new variable: Year

```{r}
read_excel("data/WORLD-MACHE_Gender_6.8.15.xls", "Sheet1", col_names=T) %>%
	select(iso3, contains("matleave"), -contains("wrr")) %>%
	filter(matleave_13==5, matleave_95!=5) %>%
	pivot_longer(names_to = "year", cols = 2:20, values_to = "degree") %>%
	replace_na(list(degree=0)) %>%
	mutate(year2=as.POSIXct(strptime(year, "matleave_%y"))) %>%
	mutate(year3 = strftime(year2, "%Y")) %>% View
```

## 7. Plotting: bar chart

```{r}
read_excel("data/WORLD-MACHE_Gender_6.8.15.xls", "Sheet1", col_names=T) %>%
	select(iso3, contains("matleave"), -contains("wrr")) %>%
	filter(matleave_13==5, matleave_95!=5) %>%
	pivot_longer(names_to = "year", cols = 2:20, values_to = "degree") %>%
	replace_na(list(degree=0)) %>%
	mutate(year2=as.POSIXct(strptime(year, "matleave_%y"))) %>%
	mutate(year3 = strftime(year2, "%Y")) %>%
	ggplot() +
	aes(year3, degree) +
    geom_col(color="royalblue", fill="royalblue") + 
	facet_wrap(~ iso3) + 
    theme_void()
```
