---
title: "R05_5_ptt_demo_prac"
author: "Jilung Hsieh"
date: "2019/6/3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading library
- dplayr, time, word tokenization, string processing, text mining, and stringAsFactors
```{r}

```



# Loading data
- two rda files in the pttdata directory
```{r}

```


# Loading jieba cutter
```{r}
segment_not <- c("韓國瑜")
cutter <- worker()
new_user_word(cutter, segment_not)
stopWords <- readRDS("data/stopWords.rds")
```


# Filtering out posts not in the topic

## Detecting keywords to observe
`f(x)segment(x, cutter))`
```{r}

```

## Cleaning and reformatting data
- converting time stamp `as.POSIXct(strptime(time, pattern))`
- getting poster id by regular expression str_replace(str, "to replace", "replace-r")
- filtering out unessential keywords
- filtering out na
- filtering out ill-formatted ip address
```{r}

```


## Taking a glance at time span
```{r}

```

## Taking a glance at time span cutted by week
- `mutate(week = cut(ptime, breaks = "week"))`
```{r}

```


# Detecting questionable ip
## Questionable IP and User mapping
- poster_id1 -> n1 -> ip -> n2 -> poster_id2

```{r}


```

## Looking up ip location
```{r}
# devtools::install_github("gitronald/IPtoCountry")
library(IPtoCountry)
data(IPs)
```


## building ip2country mapping
```{r}

```

## Joining questionable IP and it location
```{r}

```


## Plotting temporal features: hour by weekdays

```{r}


```


## Joining comments and post data
```{r}

```

## Calcultaing responding time as a feature
```{r}

```


# Drawing network

## Getting sub-graph
```{r}
toplot <- comment2post.df %>%
    filter(!is.na(ptime)) %>%
    count(commentor, poster_id) %>%
    arrange(-n) %>%
    slice(1:200)
```


## Drawing network
```{r}
library(igraph)
g <- graph_from_data_frame(toplot, directed = FALSE) 
Isolated = which(degree(g)==0)
g = delete.vertices(g, Isolated)
g <- simplify(g, remove.loops = T, 
              remove.multiple = F)

?simplify
E(g)$n
V(g)$size = centralization.degree(g)$res + 1

E(g)$weight <- E(g)$n
is.weighted(g)

# E(g)$weight

l <- layout_with_kk(g)
# l <- layout_with_mds(g)  
# l <- layout_with_fr(g)
# l <- layout_with_sugiyama(g)
# l <-  layout_with_lgl(g)
# l <- layout_with_circle(g)
# l <- layout_with_gem(g) # GEM force-directed



# pdf("plot.pdf",10,10)
plot(g, vertex.label = V(g)$name,  
     edge.curved = 0.2,
     vertex.label.cex = sqrt(V(g)$size)/8,
     vertex.size  = sqrt(V(g)$size),
     edge.arrow.size = 0, 
     layout = l,
     edge.width = log10(E(g)$n - min(E(g)$n) + 1),
     vertex.label.family = 'Heiti TC Light',
     edge.color = rgb(0.5,0.5,0.5,0.5))
# dev.off()
```

# Draw network by ggraph
```{r}
library(ggraph)
set.seed(2017)

ggraph(g, layout = "fr") +
  geom_edge_link() +
  geom_node_point() +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1)


ggraph(g, layout = "kk") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE) +
  geom_node_point(color = "lightblue", size = 5) +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1, color = "blue", alpha = 0.5) +
  theme_void()

```





