---
title: "R06_4_tw_map_sf"
author: "Jilung Hsieh"
date: "2019/8/27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading packages

```{r message=FALSE, warning=FALSE, include=FALSE}
options(stringsAsFactors = F)
library(sf)
library(tidyverse)
library(ggplot2)
```

# Loading county-level president voting rate

```{r}
president_vote <- readxl::read_xlsx('twdata/president.xlsx') %>% 
  mutate(total = chu + tsai + song) %>% 
  mutate(chu_ratio = chu / total,
         tsai_ratio = tsai / total,
         song_ratio = song / total,
         tsai_chu_ratio = tsai / chu)
```

# sf to load county level shp

<https://fidanalytics.co.uk/blog/simplifying-polygons-r>

```{r}
# install.packages("sf")
# install.packages("rmapshaper")
county_sf <- st_read("shapefiles/COUNTY_MOI_1090820.shp")
# county_sf <- st_read("shapefiles/county.shp")
# plot(county_sf) # Taking very long time

```

## Simplfying map polygon

-   Google Earth is in a Geographic coordinate system with the wgs84 datum. (EPSG: 4326)
-   Google Maps is in a projected coordinate system that is based on the wgs84 datum. (EPSG 3857)
-   The data in Open Street Map database is stored in a gcs with units decimal degrees & datum of wgs84. (EPSG: 4326)
-   The Open Street Map tiles and the WMS webservice, are in the projected coordinate system that is based on the wgs84 datum. (EPSG 3857)
-   <https://epsg.io/3825> for taiwan
-   27700 for UK
-   Explaining: <https://gis.stackexchange.com/questions/48949/epsg-3857-or-4326-for-googlemaps-openstreetmap-and-leaflet>

```{r}
county_sf <- st_read("shapefiles/COUNTY_MOI_1090820.shp")
# county_msoa <- st_transform(county_sf, 3857)
county_ms_simp <- rmapshaper::ms_simplify(county_sf,  keep=0.001) 
plot(county_ms_simp)
```

```{r}

# install.packages("rmapshaper")
st_read("shapefiles/county.shp") %>%
  # st_transform(3825) %>% #3857
  rmapshaper::ms_simplify(keep=0.01) %>%
  right_join(president_vote, by=c("COUNTYNAME"="county")) %>%
  ggplot(aes(fill = chu_ratio)) + 
  geom_sf(color="white", size=0.2) + 
  scale_fill_gradient(low = "#FFFFFF", high = "#0000FF") + 
  theme_void()
```

# Town level

## Reading income data

```{r}
taipei_income <- readxl::read_xlsx('twdata/台北各區每人所得.xlsx') 
```

## Read Taipei zip code

```{r}
twzipcode_json <- jsonlite::fromJSON("twdata/twzipcode.json")[[1]]
taipei_zipcode <- twzipcode_json %>% 
  filter(city == "台北市")
```

```{r}
# install.packages("rmapshaper")
st_read("shapefiles/TOWN_MOI_1100415.shp") %>%
    filter(COUNTYNAME == "臺北市") %>%
    # st_transform(3825) %>% #3857
    rmapshaper::ms_simplify(keep=0.05) %>%
    left_join(taipei_income, by = c("TOWNNAME" = "district")) %>%
    left_join(taipei_zipcode, by= c("TOWNNAME" = "district")) %>%
    ggplot(aes(fill = income)) + 
    geom_sf() + 
    scale_fill_gradient2(low = "#FF8888", high = "#0000AA", midpoint = median(taipei_income$income)) +
    geom_text(aes(x = lng, y = lat, label = TOWNNAME), family = "Heiti TC Light", color = "black", size = 2.5)+
    theme_void()
```
