---
title: "R03_1 Crawling 104"
author: "Jilung Hsieh"
date: "2020/10/25"
output:
  html_document:
    highlight: zenburn
    number_sections: yes
    theme: cerulean
    toc: yes
    css: style.css
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Loading essential packages
```{r}
library(tidyverse)
options(stringsAsFactors = F)



```



# Get the first page

## (try to) Load the 2nd page

```{r}
# Copy and assign the 2nd page url to url2
url2 <- 

# Copy and assign  the 3rd page url to url3
url3 <- 

# Send GET() request to get the page of url2, 
# parse it, 
# and assign it to res2

res2 <-  GET(url2) %>% 
  content("text") %>% 
  fromJSON()

# Tracing variable result2 and finding the data frame, 
# assign to df2

df2 

```



## Add "Referer" argument to request page data correctly

```{r}
response <- GET(url2, config = add_headers("Referer" = "https://www.104.com.tw/"))
res <- response %>% content("text") %>%
  fromJSON()
res$data$list %>% View
```



## Get the first page by modifying url

```{r}
# Guessing the 1st page data url to url1


# Getting back the 1st page data




```


# Combine data frames by row

## (try to) Combine two pieces of data (having exactly the same variables)

```{r}
# all.df <- bind_rows(df1, df2) # will raise error
# Error in bind_rows_(x, .id) : 
#   Argument 31 can't be a list containing data frames
```

## Drop out hierarchical variables
- Preserving numeric or character, dropping list of data.frame by assigning NULL to the variable

```{r}
# Drop list and data.frame inside the data.frame


# Re-binding two data.frames df1 and df2 by rows


```

## Dropping hierarchical variables by dplyr way
```{r}

# Getting the 1st page data and dropping variable tags and link
# Assigning to df1


# Getting the 2nd page data and dropping variable tags and link
# Assigning to df2


# binding df1 and df2


```


# Finding out the last page number
```{r}
# Tracing the number of pages in result1


# Checking the page number of the last page
# Examining if the last page data available by re-composing URL with paste0()


# Getting back and parsing the last page data



```

# Use for-loop to get all pages
```{r}





```

# Combine all data.frame
```{r}

#  The 1st url of the query


# Getting back the 1st page data


# Tracing and getting total number of page


# Truncating hierarchical variables: link and tags



# for-loop to getting back data and joining them



```







