---
title: "Parsing posts of PTT"
author: "Jilung Hsieh"
date: "`r Sys.Date()`"
output: html_document
---

# loading packages
```{r}
library(tidyverse)
library(httr)
library(rvest)
```



# Loading post list with links
```{r}
# Reading post link rds -> posts
posts <- read_rds("data/post_HatePolitics_link.rds")
posts %>% glimpse()

```


# Getting one post for examining html structure
```{r}
# WLOG, getting the first post link as an example, assign to -> url
url <- posts$link[1]
# Getting back the article and parsing as html
# Remember to send cookie
doc <- GET(url, config = set_cookies("over18" = "1")) %>%
    content("text") %>%
    read_html()



# Verifying the doc by write_html() and browseURL()
write_html(doc, "temp/test.html")
browseURL("temp/test.html")

```


# Parse one post
```{r}
# Getting content by CSS selector
pcontent <- html_node(doc, "#main-content") %>% html_text() %>% cat


# BETTER for the case, Getting content by XPath
pcontent <- html_nodes(doc, xpath = '//*[@id="main-content"]/text()') %>% 
    html_text() %>%
    str_c(collapse = "") %>%
    str_replace_all("\n", "")






# Getting metadata

metadata <- html_nodes(doc, "#main-content > div.article-metaline > .article-meta-value") %>% html_text()

ptime <- metadata[3]
pauthor <- metadata[1]
ptitle <- metadata[2]


# Combining data to a data frame
post.temp <- tibble(url, pcontent, ptitle, pauthor, ptime)

```


# Using for-loop to get all posts
```{r}

# Create an empty data frame -> all_posts

all_posts <- tibble()
# for-loop
for(url in posts$link){
    doc <- GET(url, config = set_cookies("over18" = "1")) %>%
        content("text") %>%
        read_html()   
    pcontent <- html_nodes(doc, xpath = '//*[@id="main-content"]/text()') %>%
        html_text() %>%
        str_c(collapse = "") %>%
        str_replace_all("\n", "")
    
    metadata <- html_nodes(doc, "#main-content > div.article-metaline > .article-meta-value") %>% html_text()
    
    ptime <- metadata[3]
    pauthor <- metadata[1]
    ptitle <- metadata[2]
    
    post.temp <- tibble(url, pcontent, ptitle, pauthor, ptime)
    print(url)
    
    all_posts <- bind_rows(all_posts, post.temp)
}


```

# Practice I. Crawling comments in the for-loop
Modifying the for-loop content to scraping comments for each post. Each iteration of for-loop will scrape and parse multiple comments. Try to bind them together and store all comments in another data frame names "comments."

```{r}

```



# Practice II. Cleaning variables
- Converting posts timestamp to R datetime
- Extracting id and nickname from the author field.
```{r}

```



# Practice III. Writing to rds with timestamp
- Saving posts by `write_rds()`
- Using current time as part of file name.
```{r}
# Getting current time for file name -> current_time


# Converting data type and writing rds


```



