---
title: "AS03_join_edu_data"
author: "Jilung Hsieh"
date: "10/03/2020"
output:
  html_document:
    highlight: zenburn
    number_sections: no
    theme: cerulean
    toc: yes
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
options(stringsAsFactors = F)
```

# Q1 Joining educational data
- Reading educational data from the following csv file.

## Reading education data
```{r}
read_csv("data/opendata107Y020.csv") %>%
    slice(-1) %>% 
    glimpse()
```


## Town level educational data 
- Original data is village-level data
- Using `group_by()` to create town-level statistical data.

```{r}

```


## Loading town-level age, marriage, and referendum data
- Loading previous town-level age-marriage-referendum-data

```{r}

```



## Joining data together
- Joining two town-leave data together 
- data 1: new added educational data
- data 2: previous age-marriage-referendum-data

```{r}

```

## **Q1 Ans: Joined data dimension**
- using `dim()` to display data dimension (should be 368). 
- TAs will score Q1 according to the outcome.

```{r}
# dim(YOUR_DATA_FRAME_NAME)
```


## **Q1 Ans: glimpse()**
- Using `glimpse()` to print out data you join below. 
- TAs will score Q1 according to the `glimpse()` outcome.

```{r}
# glimpse(YOUR_DATA_FRAME_NAME)
```

# Q2 Open Question - Joining one more dimension
- TASK: Collecting one more dimension from open data and join it to the above two-level data
- e.g., economic, wealth, educational resource, ...


## Read the file
```{r}

```

## Display the data dimension of the file
```{r}

```

## Add code chunks as you need


## **Q2 Ans: Answer following questions**
- Data source link (the page you download the data): 
- Describe the data source in your words: 


## **Q2 Ans: Dim() of joined data frame**

```{r}
# dim(YOUR_DATA_FRAME_NAME)
```


## **Q2 Ans: glimpse() of joined data frame**
```{r}
# glimpse(YOUR_DATA_FRAME_NAME) 
```

# Q3 Open question - Linear regression
 - Now, you have age, marriage, and education as indenpendent variables and referendum 10th agreement as the dependent variable.
 - Go online and search how to run regression with R
 - Report the regression result 

## **Q3 Ans**
```{r}

# code for print out regression result 
```



# Q4 Challenge: The median of grouped data
- Calculating age median of grouped data
- Reference: https://www.themathdoctors.org/finding-the-median-of-grouped-data/
- Solve it by dplyr pkgs
- If you can't answer the question correctly, keep your code (even wrong) to get partial scores.

## **Q4 Ans: glimpse()**
```{r}
# glimpse(YOUR_DATA_FRAME_NAME)
```

