---
title: "yt_comment_demo"
output: 
  html_document:
    code_folding: "none"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(lubridate)
options(stringsAsFactors = F)
```



# Loading data

```{r echo=TRUE}
data_url <- "https://github.com/P4CSS/R4CSSData/raw/main/newswawawa_yt_comments.rds"
raw <- read_rds(url(data_url))
```



# 1. Data Coverage: density plot

```{r}
```

# 2. Data Converage: weekly or monthly
- Hint: using `floor_date()`


```{r}

```

# 3. Demographic
- Add more demographic features here, at least more 2 features

```{r}
message("Number of videos: ", length(unique(raw$videoId)))

```


# 4. Number of comment distribution per video: density plot
Hint: using ggplot2 `xlab()` to label the x-axis

```{r}

```



# 5. Number of comments distribution
- Hint: Using `scale_y_log10()` and `scale_x_log10()` to adjust y-axis scale
- Using `geom_jitter()` to plot scatter

```{r}
    
```


# 6. Comment patterns each month
- Filter comments after 2019-09-30, before 2020-02-01 
- density plot per month
- subplot by `facet_wrap()` with argument `scales = "free"`

```{r}

```



# 7. Comments patters by week
- Filter comments after 2019-12-01, before 2020-02-01 


```{r}

```


# 8. Comments pattern by hour per day
- Filter comments after 2019-12-30, before 2020-01-20 
- may using `ifelse()` ternary operation to divide plot into two parts: after and before 2020-01-11


```{r}

```

# 9. Challenge: Growth of unique member

```{r}


```

